Mechanisms of detachment in fibrillar adhesive systems

### 2021-08-10 source/tex/manuscript.tex
abstract shortened, line numbers removed for RSIF submission.

\modulolinenumbers[5]

@@

\begin{abstract}
Several creatures can climb on smooth surfaces with the help of hairy
adhesive pads on their legs. A rapid change from strong attachment
to effortless detachment of the leg is enabled by the asymmetric geometry
of the hairs. In this study, we propose mechanisms by which
a hairy pad can be easily detached, even when the hairs possess no
asymmetry. Here, we examine the possible function of the leg joint and the claws.
Based on a spring-based model, we consider three modes
of detachment: vertically pulling the pad while maintaining either
a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
the claw. We show that in all cases, the adhesion force can be significantly
reduced due to elastic forces when the hairs deform non-uniformly
across the array, an effect that we call ``\emph{elastic weakening}''.
Our proposed model illustrates the design advantage provided by such fibrillar
adhesive systems, which not only provides strong adhesion, but also
allows easy detachment, making it suitable as organs for fast locomotion.
The presented approaches can be potentially used to switch the adhesion
state in bio-inspired fibrillar adhesives, by incorporating artificial joints and claws into their design, 
without the need of asymmetric or stimuli-responsive fibrillar structures.
\end{abstract}

@@

\linenumbers

>>>>

%\modulolinenumbers[5]

@@

\begin{abstract}
Several creatures can climb on smooth surfaces with the help of hairy
adhesive pads on their legs. A rapid change from strong attachment
to effortless detachment of the leg is enabled by the asymmetric geometry
of the hairs. In this study, we propose mechanisms by which
a hairy pad can be easily detached, even when the hairs possess no
asymmetry. Here, we examine the possible function of the leg joint and the claws.
Based on a spring-based model, we consider three modes
of detachment: vertically pulling the pad while maintaining either
a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
the claw. We show that in all cases, the adhesion force can be significantly
reduced due to elastic forces when the hairs deform non-uniformly
across the array. %, an effect that we call ``\emph{elastic weakening}''.
Our proposed model illustrates the design advantage provided by such fibrillar
adhesive systems, which not only provides strong adhesion, but also
allows easy detachment, making it suitable as organs for fast locomotion.
The presented approaches can be potentially used to switch the adhesion
state in bio-inspired fibrillar adhesives, by incorporating artificial joints and claws into their design, 
without the need of asymmetric or stimuli-responsive fibrillar structures.
\end{abstract}

@@

%\linenumbers
